MSSM-Penn-Pitt - ACC and DLPFC - DREAM - SALMON - GRCh38 - Model Selection

### 2020-04-05 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_SALMON_GRCh38.Rmd
provenance for salmon counts

---
title: "MSSM-Penn-Pitt - ACC and DLPFC - DREAM - SALMON - GRCh38 - Model Selection"
author: "Kelsey Montgomery, Gabriel Hoffman, Thanneer Perumal"
date: "`r date()`"
output: html_document
---

>>>>

---
title: "MSSM-Penn-Pitt - ACC and DLPFC - DREAM - SALMON - GRCh38 - Model Selection"
author: "Kelsey Montgomery, Gabriel Hoffman, Thaneer Perumal"
date: "`r date()`"
output: html_document
---
